The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
full numbers

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~182354, HD~189636, or HD~189750.

>>>>

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage. From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations. These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
